% This is tied to certain citations.

\def\wgtrademark{\raise.73ex\hbox{\tiny{\textregistered}}\;}
\def\wgcopyright{\raise.73ex\hbox{\tiny{\copyright}}\;}

\vskip 3cm

\begin{quote}
%%
%%  This document represents my pesonal notes about the landscape
%%  related to deploying science research in and amoung my
%%  colleagues. It is freely available, and worth every penny! While I
%%  retain copyright, this is soley to prevent its mis-appropriation for
%%  others' private or commercial uses. While an effort was made to
%%  cite every product etc some will have been missed.  This information
%%  and code snippets are provided, as is,  under the MIT license for others.
%%  
{ Copyrights and Trademarks:\\ 
\\
Arduino 2022, under Creative Commons licensing;
Anaconda is a collection of Python and analytic tools by Anaconda\wgtrademark Inc.;
Apple\wgtrademark, iOS\wgtrademark,
  OS/X\wgtrademark and Macbook\wgtrademark are a trademarks of Apple Inc., registered 
in the U.S. and other countries;
   Astrometry.net Copyright 2006-2010 Michael Blanton, David W. Hogg, Dustin Lang, 
Keir Mierle and Sam Roweis, Copyright 2011-2013 Dustin Lang and David W. Hogg. 
Copyright 2006-2022 Michael Blanton, David W. Hogg, Dustin Lang, Keir Mierle and 
Sam Roweis \cite{arXiv:0910.2233} (the Astrometry.net Team);
   The Astropy Project \cite{astropy:2018} is a loose-confederation funded by NumFOCUS, Inc.;
Docker, Inc. provides the technology for Docker Environments, Containers etc, \textcopyright 2013-2015 Docker, Inc. All rights reserved;
IRAF, PyRAF and Ureka Copyright \textcopyright 2018 Association of Universities for Research in
  Astronomy (AURA);
  Bokeh,2021 Bokeh Contributors,  is a fiscally sponsored project of NumFOCUS;
  Django The Django Software Foundation;
  NumPy   \textcopyright 2005-2018, NumPy Developers ;
  The ``Math Kernel Library'' (MKL\wgtrademark) and Intel\wgtrademark are registered
  by Intel Corporation -- Santa Clara, CA, USA;
Microsoft, ``Microsoft Windows'', WSL are registered trademark of Microsoft Corporation;
PostgreSQL\wgtrademark is a registered trademark of 
   PostgreSQL Global Development Group;
Python is Copyright \textcopyright 2001-2018 Python  Software Foundation.
   All rights reserved ;
Raspberry Pi, governed by the Raspberry Pi Foundation with offerings covered by the
Creative Commons CC BY-SA licensing;
SAOImage/ds9 and code therein is licensed through the 
   Smithsonian Astrophysical Observatory;
SExtractor \cite{web-sextractor} (Emmanuel Bertin, author) copyright
   \textcopyright 2010 IAP - CNRS / Universite P.\&M.Curie ;
Ubuntu \textcopyright 2015 Canonical Ltd. Ubuntu and Canonical are registered 
  trademarks of Canonical  Ltd;
UNIX\wgtrademark is a registered trademark in
  the United States and other countries, licensed exclusively through
  X/Open Company Ltd;
  Linux\wgtrademark is the registered trademark of Linux Mark Institute,
  on behalf of Linus Torvalds, in the U.S. and other countries.
  \\
  ~
}



\end{quote}
{\tiny
Copyright \wgcopyright (2020) Wayne Green. All rights reserved.

Permission is hereby granted, free of charge, to any person obtaining
a copy of this software and associated documentation files (the
"Software"), to deal in the Software without restriction, including
without limitation the rights to use, copy, modify, merge, publish,
distribute, sublicense, and/or sell copies of the Software, and to
permit persons to whom the Software is furnished to do so, subject to
the following conditions:

The above copyright notice and this permission notice shall be
included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE
LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION
OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION
WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
}
